---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# granovaGG

<!-- badges: start -->

<!-- badges: end -->

The package granovaGG is designed to produce statistical graphics driven by the fundamental questions of analysis of variance.
The graphics granovaGG creates can offer far more visual information than a traditional tabular model summary or significance test.
For an example of how granovaGG can enhance analysis, see [Pruzek and Helmreich (2009)](rmpruzek.com/wp-content/uploads/2011/07/ElementalGraphicsForANOVA.finalJune11.pdf).

## Installation

You can install the development version of granovaGG from [GitHub](https://github.com) with:

``` r
# install.packages("devtools")
devtools::install_github("briandk/granovaGG")
```

## Usage

There are three main functions in this package:

-   `granovagg.1w()`: for plotting one-way analysis of variance (ANOVA)

-   `granovagg.ds`(): for plotting dependent-sample t-test data

-   `granovagg.contr()`: for plotting contrasts

## Examples

### `granovagg.1w()`

```{r}
library(granovaGG)
data(poison)

# Note violation of constant variance across groups in following graphic.
granovagg.1w(poison$SurvTime, group = poison$Group, ylab = "Survival Time")
```

### `granovagg.ds()`

```{r}
library(granovaGG)

# This example corresponds to case 1b in Pruzek and Helmreich (2009). In this
# graphic we're looking for the effect of Family Treatment on patients with anorexia.

data(anorexia.sub)

granovagg.ds(anorexia.sub,
             revc = TRUE,
             main = "Assessment Plot for weights to assess\nFamily Therapy treatment for Anorexia Patients",
             xlab = "Weight after therapy (lbs.)",
             ylab = "Weight before therapy (lbs.)"
)    
```

### `granovagg.contr()`

```{r}
data(arousal)  
contrasts22 <- data.frame( c(-.5,-.5,.5,.5), 
  c(-.5,.5,-.5,.5), c(.5,-.5,-.5,.5) )
names(contrasts22) <- c("Drug.A", "Drug.B", "Drug.A.B")
granovagg.contr(arousal, contrasts = contrasts22)
```

## FAQs
