---
title: "Customizing granovaGG Graphics with ggplot2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customizing granovaGG Graphics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

```{r setup}
library(granovaGG)
library(ggplot2)
```

## Why customize?

Each `granovagg.*()` function returns a `ggplot` object (or a list of them).
That means you can layer additional geoms, replace scales, or swap themes
exactly as you would with any other `ggplot2` graphic. This vignette walks
through a few common patterns so you can adapt the package's defaults to match
your publication or presentation style.

## One-way ANOVA example

The `granovagg.1w()` helper returns a single `ggplot`. Here we hide the
diagnostic square annotations (to reduce clutter) and then add a custom fill
palette, swap in `theme_minimal()`, and relabel the axes.

```{r one-way, warning=FALSE, message=FALSE}
data("poison", package = "granovaGG")

one_way <- granovagg.1w(
  data = poison$SurvTime,
  group = poison$Group,
  print.group.summary = FALSE,
  print.model.summary = FALSE,
  print.squares = FALSE
)

one_way +
  scale_fill_manual(values = c("Group Means" = "#0d6efd")) +
  labs(
    x = "Group contrast (custom label)",
    y = "Survival time (days)",
    title = "granovagg.1w graphic with a minimal theme"
  ) +
  theme_minimal()
```

Because `granovagg.1w()` adds named color/fill scales, you can target specific
legend entries (such as `"Group Means"`) when overriding palettes.

## Contrast panels

`granovagg.contr()` returns a list of plots (one per contrast plus the summary
panel). The objects in that list are ready for additional layers. Below we add
a reference line and change the color palette for the first contrast panel.

```{r contrast, warning=FALSE, message=FALSE}
data("arousal", package = "granovaGG")
contrasts22 <- data.frame(
  c(-0.5, -0.5, 0.5, 0.5),
  c(-0.5, 0.5, -0.5, 0.5),
  c(0.5, -0.5, -0.5, 0.5)
)
names(contrasts22) <- c("Drug.A", "Drug.B", "Drug.A.B")

contrast_plots <- granovagg.contr(
  arousal,
  contrasts = contrasts22,
  jj = 0.2,
  xlab = c("Drug A vs placebo", "Drug B vs placebo", "Interaction")
)

contrast_plots[[1]] +
  geom_hline(yintercept = 24, color = "#d62728", linewidth = 0.4, linetype = "dashed") +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "Overlaying custom reference lines",
    subtitle = "Contrast panel 1 with an extra dashed threshold"
  )
```

Since `granovagg.contr()` exposes the plots as a plain list, you can store them,
modify individual panels, and print the customized versions wherever you like.

## Dependent sample graphic

The dependent-sample helper (`granovagg.ds()`) also returns a `ggplot`. Because
the returned object retains all of the original aesthetics you can alter the
point style, swap color scales, or apply themes to match other figures in your
report.

```{r ds, warning=FALSE, message=FALSE}
data("anorexia.sub", package = "granovaGG")

ds_plot <- granovagg.ds(
  anorexia.sub,
  plot.theme = theme_granova_ds,
  southwest.padding = 0.05,
  northeast.padding = 0.05
)

ds_plot +
  geom_point(
    data = anorexia.sub,
    aes(x = Prewt, y = Postwt),
    color = "#2ca02c",
    alpha = 0.6,
    size = 2
  ) +
  theme_bw() +
  labs(
    title = "Augmenting the dependent-sample plot",
    subtitle = "Adding a second scatter layer and switching themes"
  )
```

Feel free to experiment with annotations (`annotate()`), facetting, guide
adjustments, or any other `ggplot2` extension. If you already have an
institutional theme, you can apply it directly to the plots generated by
`granovaGG`.
